Formal Modelling of Predator Preferences using Molecular Gut-Content Analysis

### 2015-05-19 paper/main.tex
final touches discussion; v1.1 ready for CRAN

Our methods offer ecologists a formal statistical framework to model and test predators prey preferences across an array of time points and prey species.  Because we build from intuitive assumptions and well behaved statistical distributions, we were able to extend our methods to unobserved count data.  For both cases, observed or unobserved count data, a computationally efficient likelihood ratio test provides the most powerful test one can hope for.  No methods before have offered such abilities.  These methods are available to researchers via the \texttt{R} package \texttt{spiders}.

% An \texttt{R} package, named \texttt{spiders}, is available on CRAN at \url{http://cran.r-project.org/web/packages/spiders/index.html} and fits all the methods discussed above.  \nocite{Wickham:2011a,Wickham:2011,Bischl:2014}

>>>>

The methods we have presented offer ecologists a formal statistical framework to model and test predators feeding preferences across an array of time points and prey species. Building from intuitive assumptions, we have developed methodologies for analyzing counts of prey items consumed and have extended these methods for analyzing simple presence/absence data. We have provided computationally efficient methods for fitting these models using the EM algorithm and developed powerful tests for a hierarchy of hypotheses based on the likelihood ratio. We are not aware of previous methods that have offered such abilities. These methods are available to researchers via the R package spiders which is available at \url{http://cran.r-project.org/web/packages/spiders/index.html}.

\nocite{Wickham:2011a,Wickham:2011,Bischl:2014,Roualdes:2014}
